Verifying Demonstrations

### 2018-05-25 paper/intro.tex
Comments in intro

\emph{Limitations and assumptions.} Some of the assumptions that are required 
for implementing our proposition are not yet realized (see \cref{assumptions} 
for more detailed descriptions). In particular, not all (or even many) 
protesters, especially in countries with oppressive regimes, currently possess 
smartphones.
In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials. 
\seb{maybe to prevent the above issue, we could require the individual to 
  generate his secret key and only use the authority to obtain a certification 
  on his public key (in the spirit of blind signature)}
In this case, it does not make sense to verify any pro-government protests in 
which Grace's authoritarian regime wants to organize a pro-regime protest to 
demonstrate its wide support, 
\eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Finally, achieving distance-bounding protocols on smartphones is currently not 
feasible within a meaningful range of distance needed for our scenario.
They lack the required hardware to do the distance bounding fast enough.

>>>>

\emph{Limitations and assumptions.} Some of the assumptions that are required 
for implementing our proposition are not yet realized (see \cref{assumptions} 
for more detailed descriptions). In particular, not all (or even many) 
protesters, especially in countries with oppressive regimes, currently possess 
smartphones.
In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials. 
\seb{maybe to prevent the above issue, we could require the individual to 
  generate his secret key and only use the authority to obtain a certification 
  on his public key (in the spirit of blind signature)}
\daniel{That's what we currently do.
  But the government is the authority, so the government can generate and 
  certify its own keys.}
In this case, it does not make sense to verify any pro-government protests in 
which Grace's authoritarian regime wants to demonstrate its wide support, 
\eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Finally, achieving distance-bounding protocols on smartphones is currently not 
feasible within a meaningful range of distance needed for our scenario.
They lack the required hardware to do the distance bounding fast enough.
